### 2024-07-26 paper.tex
find intersection of one slodowy slice with nilpotent elts

\subsection{Finding the previous Slodowy slices}
First we find \(\ker \ad_f\).
We have \((fX)_{ij} = i (n - i) A_{i + 1,j}\), and \((Xf)_{ij} = (j - 1) (n - (j - 1)) A_{i, j - 1}\).
So, for all \(i, j \in \{1, ..., n\}\), we have 
\[i(n - i)A_{i + 1,j} = (j - 1)(n - (j - 1))A_{1, j - 1}.\]
Taking \(j = 1\), we find that \(A_{i,1} = 0\) for \(i \geq 2\).
Then, taking \(j > 1\), we find that for \(i, j \in \{1, ..., n - 1\}\),
\[A_{i + 1, j + 1} = \frac{(j - 1)(n - (j - 1))}{i(n - i)} A_{ij}.\]
So, \(\ker\ad_f\) is the set of matrices which are upper triangular and satisfy the above condition.
\par To find the Slodowy slice associated to the previous \(\spl_2\)-triple \((E, H, F)\), we just need to find \(\ker\ad_F\).
We have 
\[[F, X] = \begin{pmatrix}
    0 & 0 \\
    f X_{21} & fX_{22}
\end{pmatrix} - \begin{pmatrix}
    0 & X_{12} f\\
    0 & X_{22} f
\end{pmatrix}.\]
Thus, \(X_{21}\) must be all zeroes except for the first row, and \(X_{12}\) must be all zeroes except for the last column, and \(X_{22} \in \ker\ad_f\).
This describes \(\ker\ad_F\).

>>>>

\subsection{Finding the previous Slodowy slices}
First we find \(\ker \ad_f\).
We have \((fX)_{ij} = i (n - i) A_{i + 1,j}\), and \((Xf)_{ij} = (j - 1) (n - (j - 1)) A_{i, j - 1}\).
So, for all \(i, j \in \{1, ..., n\}\), we have 
\[i(n - i)A_{i + 1,j} = (j - 1)(n - (j - 1))A_{i, j - 1}.\]
Taking \(j = 1\), we find that \(A_{i,1} = 0\) for \(i \geq 2\).
Then, taking \(j > 1\), we find that for \(i, j \in \{1, ..., n - 1\}\),
\[A_{i + 1, j + 1} = \frac{(j - 1)(n - (j - 1))}{i(n - i)} A_{ij}.\]
So, \(\ker\ad_f\) is the set of matrices which are upper triangular and satisfy the above condition.
\par To find the Slodowy slice associated to the previous \(\spl_2\)-triple \((E, H, F)\), we just need to find \(\ker\ad_F\).
We have 
\[[F, X] = \begin{pmatrix}
    0 & 0 \\
    f X_{21} & fX_{22}
\end{pmatrix} - \begin{pmatrix}
    0 & X_{12} f\\
    0 & X_{22} f
\end{pmatrix}.\]
Thus, \(X_{21}\) must be all zeroes except for the first row, and \(X_{12}\) must be all zeroes except for the last column, and \(X_{22} \in \ker\ad_f\).
There is no restriction on \(X_{11}\).
This describes \(\ker\ad_F\).

\begin{lemma}
    Let \(J\) be a jordan block with zeroes along the diagonal, and let  \(A\) be upper triangular and nonzero.
    Then \(J + A\) is not nilpotent.
\end{lemma}
\begin{proof}
    It is straightforward to show by induction that if \(v_i = 0\) for \(i < j\), and \(v_j \neq 0\), then \(((J + A)^k v_j)_{j + k} = v_j\).
    Let \(i\) be such that \(Ae_i \neq 0\).
    Then \((J + A)^{i - 1} e_1\) has nonzero \(e_i\)-component.
    Then \((J + A)^i e_1\) has some nonzero \(e_{i'}\)-component for some \(i' \leq i\).
    Then \((J + A)^{i + (n - i')} e_1\) has some nonzero \(e_n\)-component.
    And \(i + (n - i') \geq n\), so we're done.
\end{proof}
